A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

Four upscaling techniques are investigated in this work. Arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques. The third is a randomly generated permeability field with a Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie  base case). The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability field.

>>>>

Four upscaling techniques are investigated in this work, arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques. The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie base case). The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability distribution.
